The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-07-30 paper/ms.tex
text about tables and figure

We selected as our sample all stars on-silicon in \kepler with $Kp<9$ which were unobserved for more than $8$ quarters, including those stars which were entirely unobserved. A number of these lay just at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded. After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} in order of their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, the quarters for which they were observed, the seasons for which they were on silicon (some did not even land on silicon for all seasons) and whether spectroscopy is available as in Section~\ref{spectroscopy} and Table~\ref{stellar_props}. Aside from the restriction on stars falling on the edge of a chip, the addition of these objects to conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=8$.

@@

\caption{\label{hrdiagram}
Hertzsprung-Russell diagram of the Smear Campaign stars (orange and teal) situated in the entire \kepler sample (black), using the Bedell \url{gaia-kepler.fun} crossmatch and \gaia~DR2 calibrated distances from \citet{gaiadists}. The smear sample includes giants and hot main-sequence stars. Those giants for which TRES spectroscopy have been obtained are highlighted in teal.}
\end{figure*}

>>>>

We selected as our sample all stars on-silicon in \kepler with $Kp<9$ which were unobserved for more than $8$ quarters, including those stars which were entirely unobserved. A number of these lay just at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded. After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} in order of their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, \gaia~DR2 source identifiers, apparent~$G$ magnitudes and distances from \citet{gaiadists}, the quarters for which the stars were observed, the seasons for which they were on silicon (some did not even land on silicon for all seasons), and whether spectroscopy is available as in Section~\ref{spectroscopy} and Table~\ref{stellar_props}. Aside from the restriction on stars falling on the edge of a chip, the addition of these objects to conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$. In Figure~\ref{hrdiagram} we show these stars on a colour-magnitude diagram in \gaia $Bp-Rp$ and absolute~$G$ magnitudes using \gaia~DR2 calibrated distances from \citet{gaiadists}, and situate these in context with the entire \kepler sample from the Bedell \url{gaia-kepler.fun} crossmatch.

@@

\caption{\label{hrdiagram}
\gaia colour-magnitude diagram of the Smear Campaign stars (orange and teal) situated in the entire \kepler sample (black), using the Bedell \url{gaia-kepler.fun} crossmatch and \gaia~DR2 calibrated distances from \citet{gaiadists}. The smear sample includes giants and hot main-sequence stars. Those giants for which TRES spectroscopy have been obtained are highlighted in teal.}
\end{figure*}
